Excuse me, do you have a moment to talk about version control?

### 2017-10-05 README.Rmd
Remove "Yes, "
Replace a chatty word ("slick") with a more formal word ("polished")

The Git way is to track the evolution of `iris.R`, through a series of commits,
each equipped with an explanatory message. Figure \ref{fig:diy-vs-git}C depicts this linear, *in situ* process, with development and time flowing from bottom to top. Figure \ref{fig:diy-vs-git}D shows the same history for a common collaborative Git workflow, where contributors work independently but sync regularly to a common version. Especially important versions get a human-readable tag, e.g., "draft-01", to signal a meaningful milestone. Yes, there is some pain in adopting the formalism of Git, but it is worth it.

@@

We've introduced Git's powerful structure for file management, so where does GitHub fit in? GitHub complements Git by providing a slick user interface and distribution mechanism for Git repositories. Git is the software you will use locally to record changes to a set of files. GitHub is a hosting service that provides a Git-aware home for such projects on the internet. These relationships are shown in Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google Drive, but more structured, powerful, and programmatic.

>>>>

The Git way is to track the evolution of `iris.R`, through a series of commits,
each equipped with an explanatory message. Figure \ref{fig:diy-vs-git}C depicts this linear, *in situ* process, with development and time flowing from bottom to top. Figure \ref{fig:diy-vs-git}D shows the same history for a common collaborative Git workflow, where contributors work independently but sync regularly to a common version. Especially important versions get a human-readable tag, e.g., "draft-01", to signal a meaningful milestone. There is some pain in adopting the formalism of Git, but it is worth it.

@@

We've introduced Git's powerful structure for file management, so where does GitHub fit in? GitHub complements Git by providing a polished user interface and distribution mechanism for Git repositories. Git is the software you will use locally to record changes to a set of files. GitHub is a hosting service that provides a Git-aware home for such projects on the internet. These relationships are shown in Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google Drive, but more structured, powerful, and programmatic.
